---
  title: "BIOS 611 HW3 Exploratory Analysis, tibbles, and data import (Chapters 7, 10, and 11.2)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This homework is due `Monday September 17th by 6pm`.  
  Both `.Rmd` and `.html` files should be submitted.  
  (This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.)
  
    ```{r, include = FALSE}
    library(tidyverse)
    ```


# Exercise 1

1.  Explore the distribution of `price`. Do you discover anything unusual
    or surprising? (Hint: Carefully think about the `binwidth` and make sure
    you try a wide range of values.)

    Answer: 

    ```{r}

    ```

2.  Compare and contrast `coord_cartesian()` vs `xlim()` or `ylim()` when
    zooming in on a histogram.
    
    Answer: 

    ```{r}

    ```

# Exercise 2

    
1.  There are several ways of getting complete data (i.e. ignoring the incomplete cases). 
    Using each of the following functions, try to get complete data.
    
    Answer: 

    ```{r}
    # Use this dataset
    data.a = data.frame(no = 1:5, abc = letters[1:5], ABC = LETTERS[11:15], rand = rnorm(5))
    data.a[3,3] <- data.a[2,1] <- NA
    data.a
    
    # A. na.omit
    
    # B. complete.cases
    
    ```

2.  What does `na.rm = TRUE` do in `mean()` and `sum()`?

    Answer: 

    ```{r}
    
    ```


3.  We want to see if there is a pattern of delay according to the scheduled departure time.
    Criticize the following graph. (If you cannot notice the problem, go back to the example in
    the note and see why they used `mutate` function. Note only a small sample was used for
    convenience.)
    
    ```{r}
    set.seed(1)
    newdata = sample_n(nycflights13::flights, 1000)
    newdata %>% ggplot(aes(sched_dep_time, dep_delay)) + geom_point()
    ```

    Answer:
    

# Exercise 3

1.  Use what you've learned to improve the visualisation of the departure times
    of cancelled vs. non-cancelled flights. (Hint: normalize them.)

    Answer: 

    ```{r}

    ```

2.  What variable in the diamonds dataset is most important for predicting
    the price of a diamond? How is that variable correlated with cut?
    Why does the combination of those two relationships lead to lower quality
    diamonds being more expensive?

    Answer: 

    ```{r}

    ```

3.  Install the ggstance package, and create a horizontal boxplot. (Use `geom_boxploth()`.)
    How does this compare to using `coord_flip()` in terms of syntax?
    
    Answer: 

    ```{r}

    ```


# Exercise 4

1.  How could you rescale the count dataset (`diamonds %>% count(color, cut)`) 
    to more clearly show the distribution of cut within colour, or colour within cut?

    Answer: 

    ```{r}

    ```

2.  Use `geom_tile()` together with dplyr to explore how average flight
    delays vary by destination and month of year.  (Hint: Summarize the data first.)
    What makes the plot difficult to read? How could you improve it (an open question)?

    Answer: 

    ```{r}
    # nycflights13::flights
    
    ```

3.  Why is it slightly better to use `aes(x = color, y = cut)` rather
    than `aes(x = cut, y = color)` in the following example (an open question)?

    ```{r}
    diamonds %>% 
      count(color, cut) %>%  
      ggplot(mapping = aes(x = color, y = cut)) +
        geom_tile(mapping = aes(fill = n))
    ```

    Answer: 

# Exercise 5

1.  Instead of summarising the conditional distribution with a boxplot, you
    could use a frequency polygon. What do you need to consider when using
    `cut_width()` vs `cut_number()`? How does that impact a visualisation of
    the 2d distribution of `carat` and `price`?

    Answer: 

    ```{r}

    ```

2.  Visualise the distribution of carat, partitioned by price. (Hint: consider a boxplot)

    Answer: 

    ```{r}

    ```

3.  How does the price distribution of very large diamonds compare to small 
    diamonds? Is it as you expect, or does it surprise you?
    (Hint: Assuming you want to do a linear regression, is there any violation?)
    
    Answer: 

    ```{r}

    ```

4.  Combine two of the techniques you've learned to visualise the 
    joint distribution of cut, carat, and price.

    Answer: 

    ```{r}

    ```

5. Two dimensional plots reveal outliers that are not visible in one 
   dimensional plots. For example, some points in the plot below have an 
   unusual combination of `x` and `y` values, which makes the points outliers 
   even though their `x` and `y` values appear normal when examined separately.
  
    ```{r, dev = "png"}
    ggplot(data = diamonds) +
      geom_point(mapping = aes(x = x, y = y)) +
      coord_cartesian(xlim = c(4, 11), ylim = c(4, 11))
    ```
    
    Why is a scatterplot a better display than a binned plot for this case?

    Answer: 

    ```{r}

    ```


# Exercise 6

1.  Compare and contrast the following operations on a `data.frame` and 
    equivalent tibble. What is different? Why might the default data frame
    behaviours cause you frustration?
    
    ```{r, eval = FALSE}
    df <- data.frame(abc = 1, xyz = "a")
    df$x
    df[, "xyz"]
    df[, c("abc", "xyz")]
    ```

    Answer: 

    ```{r}

    ```

2.  If you have the name of a variable stored in an object, e.g. `var <- "mpg"`,
    how can you extract the reference variable from a tibble?
    For example, you simply could have done `mtcars$mpg`. But later on if you 
    want to extract other variables as well, say `cyl`, which is given as an object
    `var`, you don't want to manually put the variable names by typing `mtcars$cyl`.
    How would you do this without explicitly writing `"mpg"` or `"cyl"`?

    Answer: 

    ```{r}
    newdata <- `as.tibble(mtcars)'
    var <- "mpg"
    
    

    ```

3.  Practice referring to non-syntactic names in the following data frame by:
  
    ```{r}
    newdata = tibble(`1` = rnorm(1:5), `2` = `1` + runif(5))
    ```

    1.  Extracting the variable called `1`.

    Answer: 

    ```{r}

    ```

    2.  Plotting a scatterplot of `1` vs `2`.

    Answer: 

    ```{r}

    ```

    3.  Creating a new column called `3` which is `2` divided by `1`.
        
    Answer: 

    ```{r}

    ```

    4.  Renaming the columns to `one`, `two` and `three`. 

    Answer: 

    ```{r}

    ```

4.  What does `tibble::enframe()` do? When might you use it?  
    (How can you simply generate a tibble of two vectors (1 2 3 ... 26, a b c ... z)?)

    Answer: 

    ```{r}

    ```


# Exercise 7

1.  What function would you use to read a file where fields were separated with  
    "|"?
    
    Answer: 

    ```{r}

    ```

2.  If you want to read a file from the third line, how would you code using `read_csv()` or
    `read_tsv()`?
    
    Answer: 

    ```{r}

    ```


3.  Sometimes strings in a CSV file contain commas. To prevent them from
    causing problems they need to be surrounded by a quoting character, like
    `"` or `'`. By convention, `read_csv()` assumes that the quoting
    character will be `"`, and if you want to change it you'll need to
    use `read_delim()` instead. What arguments do you need to specify
    to read the following text into a data frame?
    (Hint: Sometimes special characters act as a wild card. e.g. `.` represents
    any charaters, `*` stands for repetition, and so on. So,
    in order for R to recognize special characters as they are not as a wild card, 
    we need to put a back-slash `\` in front of the character.
    e.g. `\.` does not mean everything, but it means `.`)
    
    ```{r, eval = FALSE}
    "x,y\n1,'a,b'"
    ```
    
    Answer: 

    ```{r}

    ```

4.  Identify what is wrong with each of the following inline CSV files. 
    What happens when you run the code?
    
    ```{r, eval = FALSE}
    read_csv("a,b\n1,2,3\n4,5,6")
    read_csv("a,b,c\n1,2\n1,2,3,4")
    read_csv("a,b\n\"1")
    ```

    Answer: 

    ```{r}

    ```
