---
  title: "BIOS 611 HW6 Functions, vectors, and iteration (Chapter 19 - 21)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---
  (This homework is due Mon. Oct. 15th at 6 PM.)

  This set of exercise is largely taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1


1.  `dim()` function only works for objects such as matrix, array, or data frame. It returns `NULL` 
    when you apply the function to a vector or a list.
    Write a function called `dim2()` that returns dimension of an object, where the dimension is defined by 
    `dim()` for matrices, arrays, and data frames, by `length()` for vectors and lists, and by `NULL` 
    for all other classes.  
    Hint: use `if () {} else {}` statement.
    
    Answer: 

    ```{r}
    
    ```


2.  Write a function that returns the number of `.R` files of a specific folder (input: `path`). 
    Hint: use `list.files()` and `grep()` (or `str_detect()`).  
    (For those code chunks with `eval = FALSE` option, please leave the eval option as it is, 
     because the output will not be reproducible.)
    
    Answer: 

    ```{r, eval = FALSE}
    
    ```


3.  The following function was designed to convert the existing count data to a compositional data.  
    (i.e. each column is divided by its column sum.)
    The code has several problems. Criticize the code and provide a solution.

    ```{r}
    notGood <- function(mat, margin) {
      tmp <- apply(mat, 2, sum)
      mat <- mat / tmp
    }
    
    # example data
    set.seed(1)
    dat <- matrix(rpois(100, rep(1:10, each = 10)), 10)
    ```

    Answer: 

    ```{r}
    
    ```



# Exercise 2

1.  What's the difference between `if` and `ifelse()`? Carefully read the help
    and construct three examples that illustrate the key differences.
    Keywords: type of outputs, `NA`, output for `FALSE`
    
    Answer: 

    ```{r}

    ```


2.  How could you use `cut()` to simplify this set of nested if-else statements?

    ```{r, eval = FALSE}
    if (temp <= 0) {
      "freezing"
    } else if (temp <= 10) {
      "cold"
    } else if (temp <= 20) {
      "cool"
    } else if (temp <= 30) {
      "warm"
    } else {
      "hot"
    }
    ```
    
    How would you change the call to `cut()` if I'd used `<` instead of `<=`?
    What is the other chief advantage of `cut()` for this problem? (Hint:
    what happens if you have many values in `temp`?)

    Answer: 

    ```{r}

    ```


3.  What does this `switch()` call do? What happens if `x` is "e"?

    ```{r, eval = FALSE}
    switch(x, 
      a = ,
      b = "ab",
      c = ,
      d = "cd"
    )
    ```
    
    Experiment, then carefully read the documentation. 

    Answer: 

    ```{r}

    ```


# Exercise 3

1.  What does `commas(letters, collapse = "-")` do? Why?

    Answer: 

    ```{r}

    ```


2.  The default value for the `method` argument to `cor()` is 
    `c("pearson", "kendall", "spearman")`. What does that mean? What 
    value is used by default?

    Answer: 

    ```{r}

    ```



# Exercise 4

1.  Describe the difference between `is.finite(x)` and  `!is.infinite(x)`.

    Answer: 

    ```{r}

    ```


2.  Create functions that take a vector as input and returns:
    
    Answer: 

    ```{r}

    ```

    1. The last value.  Should you use `[` or `[[`?

    Answer: 

    ```{r}

    ```

    1. The elements at even numbered positions.
    
    Answer: 

    ```{r}

    ```

    1. Every element except the last value.
    
    Answer: 

    ```{r}

    ```



3.  What happens when you subset with a positive integer that's bigger
    than the length of the vector? What happens when you subset with a 
    name that doesn't exist?

    Answer: 

    ```{r}

    ```


# Exercise 5

1.  Describe the difference between `abc[[1]]` and `abc[["1"]]`.  
    Hint: You can use `abc <- list("2"=1:3, "1"=4:6)`

    Answer: 

    ```{r}

    ```


2.  What does `hms::hms(3600)` return? How does it print? What primitive
    type is the augmented vector built on top of? What attributes does it 
    use?
    
    Answer: 

    ```{r}

    ```

3.  Try and make a tibble that has columns with different lengths. What
    happens?

    Answer: 

    ```{r}

    ```

4.  Based on the definition above, is it ok to have a list as a
    column of a tibble? Provide an example, if yes.
    Answer: 

    ```{r}

    ```



# Exercise 6

1.  Write for loops to:


    1. Compute the mean of every column in `mtcars`.
    Answer: 

    ```{r}

    ```

    1. Determine the type of each column in `nycflights13::flights`.
    Answer: 

    ```{r}

    ```

    1. Compute the number of unique values in each column of `iris`.
    Answer: 

    ```{r}

    ```

    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.
    
    Think about the output, sequence, and body __before__ you start writing
    the loop.

    Answer: 

    ```{r}

    ```

2.  Eliminate the for loop in each of the following examples by taking 
    advantage of an existing function that works with vectors:
    (Do not use `apply`, `lapply`, `do.call` kind of functions, but try to use very basic functions)
    
    ```{r, eval = FALSE}
    # a.
    out <- ""
    for (x in letters) {
      out <- stringr::str_c(out, x)
    }
    
    # b.
    x <- sample(100)
    sd <- 0
    for (i in seq_along(x)) {
      sd <- sd + (x[i] - mean(x)) ^ 2
    }
    sd <- sqrt(sd / (length(x) - 1))
    
    # c.
    x <- runif(100)
    out <- vector("numeric", length(x))
    out[1] <- x[1]
    for (i in 2:length(x)) {
      out[i] <- out[i - 1] + x[i]
    }
    ```

    Answer: 

    ```{r}
    # a.
    
    # b.
    
    # c.

    ```


3.  It's common to see for loops that don't preallocate the output and instead
    increase the length of a vector at each step:
    
    ```{r, eval = FALSE}
    output <- vector("integer", 0)
    for (i in seq_along(x)) {
      output <- c(output, lengths(x[[i]]))
    }
    output
    ```
    
    How does this affect performance? Design and execute an experiment.

    Answer: 

    ```{r}

    ```

# Exercise 7

1.  Imagine you have a directory full of CSV files that you want to read in.
    You have their paths in a vector, 
    `files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)`, and now
    want to read each one with `read_csv()`. Write the for loop that will 
    load them into a single data frame. 
    (For those code chunks with `eval = FALSE` option, please leave the eval option as it is, 
     because the output will not be reproducible.)
    
    Answer: 

    ```{r, eval = FALSE}
    
    ```


2.  Write a function that prints the mean of each numeric column in a data 
    frame, along with its name. For example, `show_mean(iris)` would print:
    
    ```{r, eval = FALSE}
    show_mean(iris)
    #> Sepal.Length: 5.84
    #> Sepal.Width:  3.06
    #> Petal.Length: 3.76
    #> Petal.Width:  1.20
    ```
    
    (Extra challenge: what function did I use to make sure that the numbers
    lined up nicely, even though the variable names had different lengths?)

    Answer: 

    ```{r}

    ```

3.  What does this code do? How does it work?

    ```{r, eval = FALSE}
    trans <- list( 
      disp = function(x) x * 0.0163871,
      am = function(x) {
        factor(x, labels = c("auto", "manual"))
      }
    )
    for (var in names(trans)) {
      mtcars[[var]] <- trans[[var]](mtcars[[var]])
    }
    ```

    Answer: 

    ```{r}

    ```


# Exercise 8

1.  Write code that uses one of the `map` functions to:

    1. Compute the mean of every column in `mtcars`.
    Answer: 

    ```{r}

    ```

    1. Determine the type of each column in `nycflights13::flights`.
    Answer: 

    ```{r}

    ```

    1. Compute the number of unique values in each column of `iris`.
    Answer: 

    ```{r}

    ```

    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.

    Answer: 

    ```{r}

    ```

2.  What happens when you use the map functions on vectors that aren't lists?
    What does `map(1:5, runif)` do? Why?
    
    Answer: 

    ```{r}

    ```

3.  Rewrite `map(x, function(df) lm(mpg ~ wt, data = df))` to eliminate the 
    anonymous function. 

    Answer: 

    ```{r}

    ```
