---
title: "ggplot2_two"
author: "Matt Biggs"
output: html_document
---
## Markdown is a simple document formatting language

A cheat sheet can be found [here](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).

The really powerful thing is that code can be embedded in your document!
```{r}
library(ggplot2)
```


Notice that "cells" or "code blocks" are defined with the "```" delimiters, and the type of code you're running in curly brackets (e.g. "{r}").

You can run the code in a cell with the little green play button.

Not only is the code provided with the document, but the output is displayed too.

```{r}
ggplot(diamonds, aes(x=cut, y=carat)) +
  geom_violin()
```

You can modulate whether code, output, or warnings are run or displayed.

```{r eval=FALSE}
ggplot(diamonds, aes(x=cut, y=carat)) +
  geom_violin()
```

## You can include R code in your text

The easiest way to do math like "4 + 5 = `r 4 + 5`" is the let the computer handle it.

## You can include special symbols using the `$` operator.

$\sum_{n=1}^{10} n^2$