---
title: "who_functions"
author: "Matthew Biggs"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

First, let's get the WHO suicide data for 2016
All values are displayed as suicides per 100,000 people.

```{r message=FALSE}
# http://apps.who.int/gho/data/node.main.MHSUICIDE10YEARAGEGROUPS?lang=en
who_df = read_csv(url("http://apps.who.int/gho/athena/data/GHO/SDGSUICIDE?filter=COUNTRY:*;REGION:*;AGEGROUP:YEARS10-19;AGEGROUP:YEARS20-29;AGEGROUP:YEARS30-39;AGEGROUP:YEARS40-49;AGEGROUP:YEARS50-59;AGEGROUP:YEARS60-69;AGEGROUP:YEARS70-79;AGEGROUP:YEARS80PLUS&x-sideaxis=COUNTRY;SEX&x-topaxis=GHO;YEAR;AGEGROUP&profile=crosstable&format=csv"), skip = 2) %>% 
  gather(contains("years"), key = "age_group", value = "suicide_rate")

who_df
```


Let's also download a mapping from country to continent

```{r message=FALSE}
continent_df = read_csv(url("https://raw.githubusercontent.com/dbouquin/IS_608/master/NanosatDB_munging/Countries-Continents.csv"))

continent_df
```

Let's say we want to identify the highest risk demographics in Asia.

First, how do we filter on continent data?

```{r}

```

Let's only consider individual geners, not the combination:

```{r}

```

And finally, we sort to identify the demographic most likely to commit suicide:

```{r} 

```

Suppose we wanted to do the same analysis, but for South America. 
And then Oceania?
And then Europe?

What are some reasons not to just copy paste the code and swap out continent names?

How can we wite a function to identify the most vulnerable demographic within a specific continent?

```{r}

```

So, we've written a function. Why didn't it show any results?
How do you use the function?

```{r}

```

What is the function returning?
How can we explicitly return an object, as opposed to just printing results to the console?

What if the continent variable a user enters is not spelled correctly, or 
for some other reason doesn't exist? 
How can we make errors like this impossible using `if` statements?
How are if/else commands structured?

```{r}

```

Hint(%in% operator)
How about the stopifnot command?

```{r}

```

How can we use our new function with the %>% pipe operator?

```{r}

```

How can we store the function in another file, and use it in our code right here?
Why might we want to keep the function in another file?
```{r}

```

Why should we test this function?

What files do we need in order to run tests?
What tests are important, and which might be overkill?





