---
title: "who_iteration"
author: "Matthew Biggs"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

First, let's get the WHO suicide data for 2016
All values are displayed as suicides per 100,000 people.

```{r message=FALSE}
# http://apps.who.int/gho/data/node.main.MHSUICIDE10YEARAGEGROUPS?lang=en
who_df = read_csv(url("http://apps.who.int/gho/athena/data/GHO/SDGSUICIDE?filter=COUNTRY:*;REGION:*;AGEGROUP:YEARS10-19;AGEGROUP:YEARS20-29;AGEGROUP:YEARS30-39;AGEGROUP:YEARS40-49;AGEGROUP:YEARS50-59;AGEGROUP:YEARS60-69;AGEGROUP:YEARS70-79;AGEGROUP:YEARS80PLUS&x-sideaxis=COUNTRY;SEX&x-topaxis=GHO;YEAR;AGEGROUP&profile=crosstable&format=csv"), skip = 2) %>% 
  gather(contains("years"), key = "age_group", value = "suicide_rate")

who_df
```

Let's also download a mapping from country to continent

```{r message=FALSE}
continent_df = read_csv(url("https://raw.githubusercontent.com/dbouquin/IS_608/master/NanosatDB_munging/Countries-Continents.csv"))

continent_df
```

If we want to filter the WHO data based on continent, how would we start?
```{r}

```



How can we be sure the join worked? What if a country is missing, or is mispelled?

What kind of join should we perform to capture the differentially spelled country names from both data sets?

```{r}

```


How can we match up Countries with slight variations in spelling so that the join works better?






Let's use the stringdist package to compare country names.
First, let's write a function to find the best match for a single Country name.

```{r}

```

```{r}

```

Let's turn this into a function.

Now, let's iterate over all the countries and apply our "best match" function.

Let's fix the join. What steps should we follow?
